Reliable feature point matching without the use of geometric constraints

### 2013-06-06 text/clustering.tex
V. 2.2

partitions as exemplified in figure \ref{fig:compare_mirror}. Here the 
cluster shown in part \ref{fig:pitts_partition} contains left window 
corners from two buildings across both images. This is an example of 
feature points that are hard to match correctly since each point will 
have several similar potential matches.

@@

	\caption{Example of a partition of keypoints in an image}

@@

	\includegraphics[width=\textwidth]{images/murals}
	\caption{Images in the mural test set}
	\label{fig:mural}

@@

1 and 4 while XL is 1 and 5. Solid line is result by \emph{MMC} while 
dashed line is result by \emph{SIFT}}

@@

\emph{Murals} dataset\footnote{Illustrated in Figure \ref{mural}}. It 
shows that \emph{MMC} and \emph{MM} is overall superior to both 
\emph{SIFT} and \emph{Isodata} which uses geometric constraints when 
tested on image pairs with no assurance of overlap depicting simple 
planar scenes. Figure \ref{fig:result_faces} illustrates the result on a 
particular image pair from the \emph{Murals} dataset. For an example of 
a real life use case \ref{fig:result_pitts} shows the results on 
potentially overlapping image pairs generated from a typical holiday 
scene with partial overlap and slight view port change. As can be seen 
in figure \ref{fig:result_viewport}, \emph{MMC} consistently outperforms 
\emph{SIFT} across different magnitudes of the viewport change. For the 
results on image 1 and 3 from the \emph{Graf} dataset, see figure 
\ref{fig:result_graf}.

@@

In terms of performance, table \ref{table:running_times} shows the 
running time of the four algorithms over $100$ image pairs of $250$px by 
$250$px. These numbers should be interpreted with the knowledge that 
much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
computationally intensive operations in C++ which renders it much 
faster.
%
\begin{savenotes}
\begin{table}
	\centering
	\small
\begin{tabular}{l*{4}{c}}
	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
	\\
	\noalign{\smallskip} 
	%
	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
\end{tabular}
\caption{Running times\footnote{As tested on a Intel(R) Core(TM) i5-3550 
CPU @ 3.30GHz with 8Gb memory}}
\label{table:running_times}
\end{table}
\end{savenotes}
%
\section{Summary}
We have addressed the problem of matching feature points without using 
geometrical constraints and proposed two algorithms \emph{Mirror Match 
(MM)} and \emph{Mirror Match with Clustering (MMC)}. The two algorithms 
share the same common idea that feature points should have better 
matches in another image than in the image they came from to be 
considered good matches and \emph{MMC} further improves on this idea by 
using the structure of the similarity graph of the feature points. We 
also address how to test the algorithms by constructing the 
\emph{Murals} dataset consisting of $8$ source image pairs and a way to 
generate testsets based on these pairs.  The proposed approach shows 
promising results on both the \emph{Murals} dataset as well as a real 
life example from the Gallagher dataset and the \emph{Graf} image set, 
beating even a method using geometrical constraints when matching image 
pairs that might not overlap.
%
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}

>>>>

partitions as exemplified in figure \ref{fig:compare_mirror}. %

@@

	\caption{Example of a partition of keypoints in an image pair. The 
		partition shown contains window corners from a building in the 
		left image and similar corners on the shirt in the right image.  

@@

%\begin{figure*}
%	\includegraphics[width=\textwidth]{images/murals}
%	\caption{Images in the mural test set}
%	\label{fig:mural}
%\end{figure*}

@@

1 and 4 while XL is 1 and 5. \emph{MMC} is represented by a solid line 
while \emph{SIFT} results are shown by a dashed line.}

@@

\emph{Murals} dataset. It shows that \emph{MMC} and \emph{MM} is overall 
superior to both \emph{SIFT} and \emph{Isodata} which uses geometric 
constraints when tested on image pairs with no assurance of overlap 
depicting simple planar scenes. Figure \ref{fig:result_faces} 
illustrates the result on a particular image pair from the \emph{Murals} 
dataset. For an example of a real life use case \ref{fig:result_pitts} 
shows the results on potentially overlapping image pairs generated from 
a typical holiday scene with partial overlap and slight view port 
change. As can be seen in figure \ref{fig:result_viewport}, \emph{MMC} 
consistently outperforms \emph{SIFT} across different magnitudes of the 
viewport change. For the results on image 1 and 3 from the \emph{Graf} 
dataset, see figure \ref{fig:result_graf}.

@@

In terms of performance, table \ref{table:running_times} shows the 
running time of the four algorithms over $100$ image pairs of $250$px by 
$250$px. These numbers should be interpreted with the knowledge that 
much of the code behind \emph{MMC} and \emph{Isodata} is implemented in 
python while \emph{MM} and \emph{SIFT} makes use of opencv to execute 
computationally intensive operations in C++ which renders it much 
faster.
%
\begin{savenotes}
\begin{table}
	\centering
	\small
\begin{tabular}{l*{4}{c}}
	Algorithm: & \emph{SIFT} & \emph{MM} & \emph{MMC} & \emph{Isodata} 
	\\
	\noalign{\smallskip} 
	%
	Running time: & 20.94s & 18.23s & 883.99s & 555.33s \\
\end{tabular}
\caption{Running times as tested on a Intel(R) Core(TM) i5-3550 CPU @ 
3.30GHz with 8Gb memory}
\label{table:running_times}
\end{table}
\end{savenotes}
%
\section{Summary}
We have addressed the problem of matching feature points without using 
geometrical constraints and proposed two algorithms \emph{Mirror Match 
(MM)} and \emph{Mirror Match with Clustering (MMC)}. The two algorithms 
share the same common idea that feature points should have better 
matches in another image than in the image they came from to be 
considered good matches and \emph{MMC} further improves on this idea by 
using the structure of the similarity graph of the feature points. We 
also address how to test the algorithms by constructing the 
\emph{Murals} dataset consisting of $8$ source image pairs and a way to 
generate testsets based on these pairs.  The proposed approach shows 
promising results on both the \emph{Murals} dataset as well as a real 
life example from the Gallagher dataset and the \emph{Graf} image set, 
beating even a method using geometrical constraints when matching image 
pairs that might not overlap.
%
\bibliographystyle{IEEEtran}
\bibliography{bibliography}
\end{document}
